Effect of Black Hole Spins on Christodoulou Memory in Binary Mergers and its implication on Observing Gravitational Wave Bursts With Memory in Pulsar Timing Array

### 2019-10-08 notes/Paper.tex
updated notes

\begin{figure}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow8MSun.pdf}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow8MSunQuadSub.pdf}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow10MSun.pdf}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow10MSunQuadSub.pdf}
	\caption{The top figure the memory growth during two weeks interval of time with solid lines. The dashed line shows the complete memory growth. The dashed red line show the memory growth computed using PN}
	\label{fig:resedualG}
\end{figure}

\begin{figure}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDaysPreFit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDaysPostfit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth5YearsDiffSpinsInDaysPrefit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth5YearsDiffSpinsInDaysPostfit.pdf}
	\caption{The top figure the memory growth during two weeks interval of time with solid lines. The dashed line shows the complete memory growth. The dashed red line show the memory growth computed using PN}
	\label{fig:resedualGrowth}
\end{figure}

\begin{figure}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/MemoryResSpinvsMass14Days.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/MemoryResSpinvsMass1825Days.pdf}
	\caption{The top figure shows the Christodolou memory growth during two weeks of observation time as a function of Mass and Spin magnitude $\chi$. The here in M time the mass of Sun. The bottom plot show a the rms timing residuals during two week period of time.}
	\label{fig:MemoryMassVsSpin}
\end{figure}
\end{widetext}
\section{CONCLUSIONS}
Observation of Christodoulou memory would be an important test of general relativity in strong field regime. Effort to detect this memory effect in low frequency band from super massive black holes have been undertaken by pulsar timing array experiments \cite{Pshirkov2010}. In these experiment the spin effect have been neglected for modeling the signal. It is highly likely that super massive black holes have significant spin due to accretion of matter from surrounding. We have seen that the spin can significantly change memory amplitude as a result it can change the timing residuals. Hence it is important to consider the spin effect while modeling the signals. The important thing for pulsar timing measurements would be the amount of memory changes over a single two weeks period of time which is shown the figure \ref{fig:MemoryMassVsSpin} as function of total mass of the binary and the spin magnitude. For a given mass and over the allowed spin range the net change in the memory amplitude can be as big as a factor of 5 which would change the SNR, or the expected event rate within a given volume, by a factor of $5^{3}=125$

>>>>

\begin{figure}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow8MSun.pdf}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow8MSunQuadSub.pdf}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow10MSun.pdf}
	\includegraphics[width=3.0in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDays10pow10MSunQuadSub.pdf}
	\caption{The figure above shows residual growth in a given interval of time. The top left plot shows this residual growth during two weeks interval of time for different spin parameter values and the top right plot shows the residual growth after subtracting a quadratic fit for maximally spinning case and a binary with $M = 10^{8}\, M_{\odot}$. The bottom figure shows the similar plot for a binary with $M = 10^{11}\, M_{\odot}$.}
	\label{fig:resedualG}
\end{figure}

\begin{figure}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDaysPreFit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth2weeksDiffSpinsInDaysPostfit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth5YearsDiffSpinsInDaysPrefit.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/ResidualGrowth5YearsDiffSpinsInDaysPostfit.pdf}
	\caption{The figure above shows residual growth in a given interval of time. The top left plot shows this residual growth during two weeks interval of time and the top right plot shows the residual growth after subtracting a quadratic fit. The bottom figure shows the similar plot for 5 years interval of time.}
	\label{fig:resedualGrowth}
\end{figure}

\begin{figure}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/MemoryResSpinvsMass14Days.pdf}
	\includegraphics[width=3.5in]{../plots/PlotfromMathematicaData/MemoryResSpinvsMass1825Days.pdf}
	\caption{The top figure shows the root mean square of post-fit timing residuals growth as a function of Mass and Spin magnitude $\chi$. The left plot shows this post-fit residual fit during two weeks interval of time and right plot shows this for 5 years interval.}
	\label{fig:MemoryMassVsSpin}
\end{figure}
\end{widetext}
\section{CONCLUSIONS}
Observation of Christodoulou memory would be an important test of general relativity in strong field regime. Effort to detect this memory effect in low frequency band from super massive black holes have been undertaken by pulsar timing array experiments \cite{Pshirkov2010}. In these experiment the spin effect have been neglected for modeling the signal. It is highly likely that super massive black holes have significant spin due to accretion of matter from surrounding. We have seen that the spin can significantly change memory amplitude as a result it can change the timing residuals. Hence it is important to consider the spin effect while modeling the signals. The important thing for pulsar timing measurements would be the amount of memory changes over a single two weeks period of time which is shown the figure \ref{fig:MemoryMassVsSpin} as function of total mass of the binary and the spin magnitude. For a given mass and over the allowed spin range the net change in the memory amplitude can be as big as a factor of 5 which would change the SNR, or the expected event rate within a given volume, by a factor of $5^{3}=125$
